---
title: 'A Replication: Adaptive Asset Allocation- ReSolve Asset Management'
author: "Matthew Kiegerl"
date: "2/18/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=2328254} {Adaptive Asset Allocation} (AAA) is a portfolio and risk management method written by Adam Butler at ReSolve Asset Management. The strategy begins by selecting the best five assets ranked on six month momentum at the close of the last trading day of the month, from a basket of ten globally diverse asset classes represented in this model as ETF tickers. AAA is weighted according to minimum variance optimization, using a covariance matrix calculated based on 126-day correlation and 20-day volatility. Rebalance AAA at the end of every month. 
\smallskip

The ten assets used in this replication and have ticker symbols:\newline

SPDR S&P 500 ETF Trust (SPY),\newline
Vanguard FTSE Europe Index Fund ETF Shares (VGK), \newline
iShares MSCI Japan ETF (EWJ),\newline
iShares, Inc. - iShares MSCI Emerging Markets ETF (EEM)\newline
Vanguard  Real Estate Index ETF (VNQ)\newline
SPDR Dow Jones International Real Estate ETF (RWX)\newline
iShares 7-10 Year Treasury Bond ETF (IEF),\newline
iShares 20+ Year Treasury Bond ETF (TLT),\newline
Invesco DB Commodity Index Tracking Fund (DBC),\newline
SPDR Gold Shares (GLD)\newline
 


```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

require(quantstrat)
require(tseries)
########### Replication of Global Tactical Asset Allocation GTAA 5 by Meb Faber ###################################################

### By: Matthew Kiegerl
  # 
  # In this illustration, I will attempt to replicate the Adaptive Asset Allocation strategy from ReSolve Asset Management
  # 
  # Step 1: Select from 5 Globally Diversified Asset Classes from the list of 10 based on 6 month momentum
  # Step 2: weight portfolio mean-var optimization every month using 6m correlations and 1 month volatilities
  # 





  # 10 major Global Asset Classes represented by ETF tickers 
  tickers <- c("SPY", # SPDR S&P 500 ETF Trust
               "VGK", # Vanguard FTSE Europe Index Fund ETF Shares
               "EWJ", # iShares MSCI Japan ETF
               "EEM", # iShares, Inc. - iShares MSCI Emerging Markets ETF
               "VNQ", # Vanguard  Real Estate Index ETF
               "RWX", # SPDR Dow Jones International Real Estate ETF 
               "IEF", # iShares 7-10 Year Treasury Bond ETF
               "TLT", # iShares 20+ Year Treasury Bond ETF 
               "DBC", # Invesco DB Commodity Index Tracking Fund
               "GLD"  # SPDR Gold Shares
  ) 
  
  
  # Store Log returns data caluclated from adjusted prices to a list
  returns <- list()
  
  for(i in 1:length(tickers)) {
    rets <- Return.calculate(Ad(get(getSymbols(tickers[i],
                                                  from = '2000-01-01', 
                                                  method = "log"))))
    colnames(rets) <- tickers[i]
    returns[[i]] <- rets
  }
  
  # cbind rets
  returns <- na.omit(do.call(cbind, returns))
  
  
  # The Adaptive Asset Allocation algorithm- ReSolve Asset Management ala KiegerlQuant
 
    
    # get monthly endpoints, apply crash prevention
    endMonth <- endpoints(returns)
    endMonth[endMonth < 1] <- 1
    endMonth[endMonth > nrow(returns)] <- nrow(returns)
    endMonth <- unique(endMonth)
    emDiff <- diff(endMonth)
    if(last(emDiff)==1) { # if the last period only has one observation, remove it
      endMonth <- endMonth[-length(endMonth)] 
    }
    
    # initialize vector holding zeroes for assets placement
    emptyVector <- data.frame(t(rep(0, length(tickers))))
    colnames(emptyVector) <- tickers[1:(length(tickers))]
    
    
    # Create List to stoe weights
    allWeights <- list()
    
      # Start loop for 6m filter
      for(i in 1:(length(endMonth)-6)) {
        
        # subset for 6m of returns- store subsetted returns data for 6 and 1 month
        retSubset <- returns[c((endMonth[i]+1):endMonth[(i+6)]),]
        emSub <- endMonth[i:(i+6)]
        sixMonths <- returns[(emSub[1]+1):emSub[7],]
        oneMonth <- returns[(emSub[6]+1):emSub[7],]
      
        # compute 6 month cumulativer returns as momentum factor
        momentums <- Return.cumulative(sixMonths)
        
        # find top five assets
        highRankAssets <- rank(momentums) >= (length(tickers) - 4) 
        
        # index the assets in top five by rank
        indx <- which(highRankAssets)
        
        # 6m correlation to match with momentum filter, 1m volatilities, calc Covariance Matrix
        correlations <- cor(sixMonths[,indx])
        volatilities <- StdDev(oneMonth[,indx]) # use last month of data for volatility rcomputation from AAA
        covariances <- t(volatilities) %*% volatilities * correlations
        
        # compute standard min vol optimization
        minVolRets <- t(matrix(rep(1, sum(highRankAssets))))
        minVolWts <- portfolio.optim(x=minVolRets, covmat = covariances)$pw
        names(minVolWts) <- colnames(covariances)
        investedAssets <- emptyVector
        investedAssets[,highRankAssets] <- minVolWts
        
        # append to list of monthly allocations
        weights <- xts(investedAssets, order.by=last(index(retSubset)))
        allWeights[[i]] <- weights
        
      }
  
    # put all weights  and returns together 
    allWeights <- do.call(rbind, allWeights)
    investedRets <- returns[,1:(length(tickers))]
  
    # compute AAA portfolio returns
    AAA <- Return.portfolio(R = investedRets, weights = allWeights)
    colnames(AAA) <- "AAA Strategy"
```
A performance metric displaying calculated average- Annual Returns, Annual Standard Deviation, Annual Sharpe Ratio- Max Drawdown and Calmar Ratio. 
\smallskip
```{r results= "show",  message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

# compute strategy statistics, Ann Rets/ Ann SD/ Ann Sharpe/ Max DD/ Calmar Ratio
  stratStats <- function(rets) {
    stats <- rbind(table.AnnualizedReturns(rets), maxDrawdown(rets))
    stats[5,] <- stats[1,]/stats[4,]
    rownames(stats)[4] <- "Max Drawdown"
    rownames(stats)[5] <- "Calmar Ratio"
    return(stats)
  }
  stratStats(AAA)

```
\newpage
Cumulative Return, Daily  Return histogram and Drawdown curve of the AAA strategy from Jun 2007 

\smallskip
```{r results= "show",  message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

 # Plot strat rets, monthly ret histogram and drawdown curve
  charts.PerformanceSummary(AAA)
```
















