---
title: 'A Replication: Composite Dual Momentum- Gary Antonacci'
author: "Matthew Kiegerl"
date: "2/5/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=2042750} {Composite Dual Momentum} uses the authors approach to measuring momentum which consists of an absolute and relative measuring process. The strategy separates the portfolio into four  "modules,"  Equities, Credit Risk, Real Estate, and Economic Stress and each module will have two assets to select from. There will also be a proxy asset to measure the momentum of the module itself, so nine assets in total. 

\smallskip
The eight assets split into their respective modules are listed below, and lastly the proxy asset.

\smallskip
\textbf{Equities}
\newline
SPDR S&P 500 ETF Trust (SPY)
\newline iShares MSCI EAFE ETF (EFA)

\smallskip
\textbf{Credit Risk}
\newline
iShares iBoxx Investment Grade Corporate Bond ETF (LQD)
\newline iShares iBoxx $ High Yield Corporate Bond ETF(HYG)     

\smallskip
\textbf{Real Estate}
\newline
Vanguard  Real Estate Index ETF (VNQ)
\newline iShares Mortgage Real Estate Capped ETF (REM)
               
\smallskip
\textbf{Economic Stress}
\newline
SPDR Gold Shares (GLD)
\newline iShares 20+ Year Treasury Bond ETF (TLT)

\smallskip
\textbf{Proxy}
\newline
SPDR Bloomberg Barclays 1-3 Month T-Bill ETF (BIL)

\bigskip
The rules to Composite Dual Momentum follow that at the end of the last trading day of the month, calculate the twelve month cumulative returns of the assets. These cumulative returns are compared for each asset to the other in the same module. Then the cumulative returns from the greater of the two assets in each module is taken and measured against the cumulative returns of the proxy asset. If the cumulative returns of the module asset is greater than the proxy's, go long the asset with a quarter weighting of your total wealth. Following is an equity curve of the strategy from 2008-present, a histogram of monthly returns and Drawdown curve.
 
\bigskip

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

require(quantstrat)

########### Replication of the Composite Dual Momentum- Gary Antonacci ###################################################

### By: Matthew Kiegerl
  # 
  # In this illustration, I replicate Composite Dual Momentum from 
  # Gary Antonacci's 2015 white paper "Risk Premia Harvesting Through Dual Momentum" 
  #
  # Composite Dual Momentum splits the portfolio into four equal quarters.
  # Each quarter has two assets that get measured against each other. 
  # The cumulative returns from the last 12 months are measured.
  # The asset with the highest cum ret is selected then measured against the proxy.
  # If cum ret from asset is greater than proxy go long asset, else go to cash.
  #
  # 
  # 





##########################          #############################

  # 9 Global Asset Classes(ETF tickers) 
  tickers <- c("SPY", # SPDR S&P 500 ETF Trust 
               "EFA", # iShares MSCI EAFE ETF
               "LQD", # iShares iBoxx Investment Grade Corporate Bond ETF
               "HYG", # iShares iBoxx $ High Yield Corporate Bond ETF
               "VNQ", # Vanguard  Real Estate Index ETF
               "REM", # iShares Mortgage Real Estate Capped ETF
               "GLD", # SPDR Gold Shares
               "TLT", # iShares 20+ Year Treasury Bond ETF
               "BIL"  # SPDR Bloomberg Barclays 1-3 Month T-Bill ETF
               )  
  

  # Get adjusted prices of tickers from 1-1-2000 on, column bind the data
  prices <- list()
  
  for(i in 1:length(tickers)) {
    
    ticker <- Ad(get(getSymbols(tickers[i], from = '2000-01-01')))
    colnames(ticker) <- tickers[i]
    prices[[i]] <- ticker
  }
  prices <- na.omit(do.call(cbind, prices))

  
  # create monthly price and return data from daily price data
  monthly.prices <- to.period(prices, period = "months", OHLC = FALSE)
  monthly.rets <- na.omit(Return.calculate(monthly.prices))
  
  
  # Set list for data storage 
  equities <- list()
  creditRisk <- list()
  realEstate <- list()
  economicStress <- list()
  momsig <- list()
  
  # loop through length of monthly ret column less 12 for momentum calc
  for (i in 1:(length(monthly.rets$SPY)-12)) {
    
    #Calc the 12 month cum returns
    twelvemonths <- monthly.rets[c(i:(i+11)),]
    momentums <- Return.cumulative(twelvemonths)
    
    
    # Set conditions for asset selection 
    # Compare momentum of assets and asset to proxy
    # Store return in respective list
    if(momentums[,1] > momentums[,2]){
      equities[[i]] <- monthly.rets[i + 12, 1]
      momsig[[i]] <- momentums[,1]
    }else{
      equities[[i]] <- monthly.rets[i + 12, 2]
      momsig[[i]] <- momentums[,2]
    }
    
    if(momsig[i] > momentums[,9]){
      equities[[i]] <- equities[i]
    }else{
      equities[[i]] <- 0
    }
    
    
    if(momentums[,3] > momentums[,4]){
      creditRisk[[i]] <- monthly.rets[i + 12, 3]
      momsig[[i]] <- momentums[,3]
    }else{
      creditRisk[[i]] <- monthly.rets[i + 12, 4]
      momsig[[i]] <- momentums[,4]
    }
    
    if(momsig[i] > momentums[,9]){
      creditRisk[[i]] <- creditRisk[i]
    }else{
      creditRisk[[i]] <- 0
    }
    
    
    if(momentums[,5] > momentums[,6]){
      realEstate[[i]] <- monthly.rets[i + 12, 5]
      momsig[[i]] <- momentums[,5]
    }else{
      realEstate[[i]] <- monthly.rets[i + 12, 6]
      momsig[[i]] <- momentums[,6]
    }
    
    if(momsig[i] > momentums[,9]){
      realEstate[[i]] <- realEstate[i]
    }else{
      realEstate[[i]] <- 0
    }
    
    
    if(momentums[,7] > momentums[,8]){
      economicStress[[i]] <- monthly.rets[i + 12, 7]
      momsig[[i]] <- momentums[,7]
    }else{
      economicStress[[i]] <- monthly.rets[i + 12, 8]
      momsig[[i]] <- momentums[,8]
    }
    
    if(momsig[i] > momentums[,9]){
      economicStress[[i]] <- economicStress[i]
    }else{
      economicStress[[i]] <- 0
    }
  }
  
  
  # Row bind the list from all the modules
  equities <- do.call(rbind, equities)
  colnames(equities) <- "Equities"
  creditRisk <- do.call(rbind, creditRisk)
  colnames(creditRisk) <- "Credit Risk"
  realEstate <- do.call(rbind, realEstate)
  colnames(realEstate) <- "Real Estate"
  economicStress <- do.call(rbind, economicStress)
  colnames(economicStress) <- "Economic Stress"
  
  
  # Sum rows(returns) of the 4 modules nd divide by 4 to get CDM strategy returns, bind the rows
  CDM_strat <- list()
  for (i in 1:length(equities)) {
      CDM_strat[[i]] <- sum(as.numeric(c(equities[i,], creditRisk[i,], realEstate[i,], economicStress[i,])))/4
  }
  CDM_strat <- do.call(rbind, CDM_strat)
  colnames(CDM_strat) <- "CDM"
  
  # put all the data in the same dataframe
  CMD_XTS <- merge(monthly.rets[13:length(monthly.rets$SPY)], CDM_strat)
  
  # Chart using performance analytics 
  charts.PerformanceSummary(CMD_XTS$CDM)
  


```
\bigskip

A performance metric calculating Annual Returns, Annual Standard Deviation, Annual Sharpe Ratio, Max Drawdown, and Calmar Ratio are presented below. 

\bigskip
```{r results= "show",  message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

# compute strategy statistics, Ann Rets/ Ann SD/ Ann Sharpe/ Max DD/ Calmar Ratio
  stratStats <- function(rets) {
    stats <- rbind(table.AnnualizedReturns(rets), maxDrawdown(rets))
    stats[5,] <- stats[1,]/stats[4,]
    rownames(stats)[4] <- "Max Drawdown"
    rownames(stats)[5] <- "Calmar Ratio"
    return(stats)
  }
  stratStats(CMD_XTS$CDM)

```












