---
title: 'A Replication: Global Tactical Asset Allocation- Meb Faber'
author: "Matthew Kiegerl"
date: "2/02/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=962461} {Global Tactical Asset Allocation} (GTAA) is Meb Faber's seminal paper on tactical asset allocation. The strategy begins by selecting from five globally diverse assets classes. If the asset is above its 10 month SMA go long asset with $20\%$ of wealth else keep the $20\%$ in cash. 
\smallskip

The five assets used in this replication and have ticker symbols:\newline

SPDR S&P 500 ETF Trust (SPY),\newline
Vanguard FTSE Europe Index Fund ETF Shares (VGK), \newline
iShares 7-10 Year Treasury Bond ETF (IEF),\newline
Vanguard  Real Estate Index ETF (VNQ)\newline
Invesco DB Commodity Index Tracking Fund (DBC),\newline


```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

require(quantstrat)
########### Replication of Global Tactical Asset Allocation GTAA 5 by Meb Faber ###################################################

### By: Matthew Kiegerl
  # 
  # In this illustration, I will attempt to replicate the Global Tactical Asset Allocation 
  # from Meb Faber at Cambria Investment Management
  # 
  # Step 1: From 5 Globally Diversified Asset Classes measure the 10 month SMA
  # Step 2: if price asset class is greater than SMA go long asset with 20% 
  # 
  #





  # 5 major Global Asset Classes represented by ETF tickers 
  tickers <- c("SPY", # SPDR S&P 500 
               "VGK", # Vanguard FTSE Europe Index
               "IEF", # iShares 7-10 Year Treasury Bond
               "VNQ", # Vanguard  Real Estate Index 
               "DBC") # Invesco DB Commodity Index

  
  # Get adjusted prices from the tickers, cbind prices
  prices <- list()
  for(i in 1:length(tickers)) {
    
    etfPrices <- Ad(get(getSymbols(tickers[i], from = '2000-01-01')))
    colnames(etfPrices) <- tickers[i]
    prices[[i]] <- etfPrices
  }
  prices <- na.omit(do.call(cbind, prices))
  
  
  # to monthly prices and calulate returns
  monthlyPrices <- to.monthly(prices, OHLC=FALSE)
  colnames(monthlyPrices) <- tickers
  retsGlobalFive <- na.omit(Return.calculate(monthlyPrices))
  
  
  # create SMA data of five assets
  # Make list, calc SMA 10 on monthly prices, Cbind List
  SMAglobal <- list()
  for(i in 1:length(tickers)) {
    
    smaPrices <- SMA(monthlyPrices[,i], 10)
    colnames(smaPrices) <- paste0("SMA_10_" , tickers[i])
    SMAglobal[[i]] <- smaPrices
  }
  SMAglobal <- na.omit(do.call(cbind, SMAglobal))
  
  
  
  # Fit monthly price data to same length as SMA data
  ratioPrices <- monthlyPrices[((length(monthlyPrices[,1])-length(SMAglobal[,1]))+1):length(monthlyPrices[,1]), ]
  
  
  # create Ratio data of five assets, make list, calc SMA 10 on monthly prices, Cbind list
  ratio <- list()
  for(i in 1:length(tickers)) {
    
    priceTOsma <- (ratioPrices[,i]/SMAglobal[,i]) - 1
    colnames(priceTOsma) <- paste0("P2SMA_" , tickers[i])
    ratio[[i]] <- priceTOsma
  }
  ratio <- na.omit(do.call(cbind, ratio))
  
  
  # create signal for ratio > 0, sig list to return T/F  
  sigs <- list()
  for(i in 1:length(tickers)) {
    
    signals <- ratio[,i] > 0
    colnames(signals) <- paste0("Sig_" , tickers[i])
    sigs[[i]] <- signals
  }
  sigs <- na.omit(do.call(cbind, sigs))


  # lag sig df to even up rows with rets in same period(months)
  # make global 5 assets ret data to same length as sig data
  lagSigs <- na.omit(lag(sigs))
  sigRets <- retsGlobalFive[((length(retsGlobalFive[,1])-length(sigs[,1]))+2) : length(retsGlobalFive[,1]), ]

  
  # multiply rets to sig list, bind table 
  GTAA5rets <- list()
  for(i in 1:length(tickers)) {
    
    returns <- lagSigs[,i] * sigRets[,i]
    colnames(returns) <- paste0("GTAA_rets_" , tickers[i])
    GTAA5rets[[i]] <- returns
  }
  GTAA5rets <- na.omit(do.call(cbind, GTAA5rets))
  
  
  # sum rows to get cum sum
  GTAA5 <- list()
  for(i in 1:length(GTAA5rets[,1])) {
    sums <- sum(GTAA5rets[i, 1:length(tickers)])
    GTAA5[[i]] <- sums
  }
  GTAA5 <- na.omit(do.call(rbind, GTAA5))
  colnames(GTAA5) <- "GTAA"

  # divide by 5 to get portfolio returns equal weight
  GTAA5df <- cbind(GTAA5rets, (GTAA5/length(tickers)))
  
```
A performance metric displaying calculated average- Annual Returns, Annual Standard Deviation, Annual Sharpe Ratio- Max Drawdown and Calmar Ratio. 
\smallskip
```{r results= "show",  message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

# compute strategy statistics, Ann Rets/ Ann SD/ Ann Sharpe/ Max DD/ Calmar Ratio
  stratStats <- function(rets) {
    stats <- rbind(table.AnnualizedReturns(rets), maxDrawdown(rets))
    stats[5,] <- stats[1,]/stats[4,]
    rownames(stats)[4] <- "Max Drawdown"
    rownames(stats)[5] <- "Calmar Ratio"
    return(stats)
  }
stratStats(GTAA5df$GTAA)
```
\newpage
Cumulative Return, Daily  Return histogram and Drawdown curve of the GTAA strategy from Dec 2006 

\smallskip
```{r results= "show",  message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

 # Plot strat rets, monthly ret histogram and drawdown curve
  charts.PerformanceSummary(GTAA5df$GTAA)
```














