---
title: 'A Replication: Robust Asset Allocation- Alpha Architect, Wes Gray'
author: "Matthew Kiegerl"
date: "2/22/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\href{https://alphaarchitect.com/2014/12/02/the-robust-asset-allocation-raa-index/} {Robust Asset Allocation}(RAA) seeks capital appreciation with downside protection written by Wes Gray at Alpha Architect. The strategy begins by taking a balanced approach to weighting a portfolio(RAAx) $40\%$ to equities, $40\%$ to real assets and $20\%$ to bonds rebalanced yearly. If RAAx's 10 month cumulative return is greater than the bond's long $50\%$ of wealth to RAAx. If RAAx is greater than the 10m SMA of RAAx, go long $50\%$ RAAx. Sum the two parts to get RAA.
\smallskip

The seven assets used in this replication and have ticker symbols:\newline

Alpha Architect U.S. Quantitative Momentum ETF (QMOM)\newline
Alpha Architect U.S. Quantitative Value ETF (QVAL)\newline
Alpha Architect International Quantitative Momentum ETF (IMOM)\newline
Alpha Architect International Quantitative Value ETF (IVAL)\newline
Vanguard Real Estate Index Fund ETF (VNQ)\newline
Invesco DB Commodity Index Tracking Fund (DBC)\newline
iShares 7-10 Year Treasury Bond ETF (IEF)
 


```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

require(quantstrat)
########### Replication of Global Tactical Asset Allocation GTAA 5 by Meb Faber ###################################################

### By: Matthew Kiegerl
  # 
  # In this illustration, I will attempt to replicate the Adaptive Asset Allocation strategy from ReSolve Asset Management
  # 
  # Step 1: Select from 5 Globally Diversified Asset Classes from the list of 10 based on 6 month momentum
  # Step 2: weight portfolio mean-var optimization every month using 6m correlations and 1 month volatilities
  # 





  # 7major Global Asset Classes represented by ETF tickers 
  tickers <- c("QMOM", # Alpha Architect U.S. Quantitative Momentum ETF
               "QVAL", # Alpha Architect U.S. Quantitative Value ETF
               "IMOM", # Alpha Architect International Quantitative Momentum ETF 
               "IVAL", # Alpha Architect International Quantitative Value ETF
               "VNQ", # Vanguard Real Estate Index Fund ETF
               "DBC", # Invesco DB Commodity Index Tracking Fund
               "IEF" # iShares 7-10 Year Treasury Bond ETF
               )

  
  
   # Get daily Adjusted Prices
  prices <- list()
  for(i in 1:length(tickers)) {
    
    ticker <- Ad(get(getSymbols(tickers[i], from = '2000-01-01')))
    colnames(ticker) <- tickers[i]
    prices[[i]] <- ticker
    
  }
  
  # Bind price columns, make monthly price and calc monthly rets
  prices <- na.omit(do.call(cbind, prices))
  monthly.prices <- to.period(prices, period = "months", OHLC = FALSE)
  monthly.rets <- na.omit(Return.calculate(monthly.prices))
  
  
  # Create the framework portfolio(RAA) for from the monthly return data
  # rebalance the portfolio yearly
  # 40% equity, 40% Real Assets, 20% Bonds
  RAAbalancedMONTHLY <- Return.portfolio(
    monthly.rets,
    weights = c(10/100, 10/100, 10/100, 10/100, 2/10, 2/10, 1/5), 
    rebalance_on = 'years')
  colnames(RAAbalancedMONTHLY) <- "RAA_Bal_RetsM"
  
  
  ### Rule 1 TMOM, RAA - Bond > 0 = 50% long of portfolio
  
  
  # Start loop to calc the ten month cumsum Rets of the RAA Bal and IEF bonds. 
  stratSig <- list()
  for(i in 1:(length(monthly.rets[,1])-9)) {
    
    # 10 months of Rets
    tenmonthsStrat <- RAAbalancedMONTHLY[c(i:(i+9)),]
    tenmonthsIEF <- monthly.rets$IEF[c(i:(i+9)),]
    
    # compute cum returns
    stratCum <- Return.cumulative(tenmonthsStrat)
    iefCum <- Return.cumulative(tenmonthsIEF)
    
    
    # Excess returns = RAA cum rets - IEF cum rets
    # If excess rets > 0 go long strat with 50%
    xRetsSig <- ((stratCum - iefCum) > 0) 
    stratSig[[i]] <- xRetsSig
    
  }# end Loop
  
  # rbind Signal(matrix) list into one column
  stratSig <- do.call(rbind, stratSig)
  
  
  # create Data Frame with signal column and RAA Bal rets make equal length
  DFxsRets <- cbind(stratSig, RAAbalancedMONTHLY[10:length(RAAbalancedMONTHLY), ])
  colnames(DFxsRets) <- c("stratSig", "RAAbalMrets")
  
  
  # Start loop, multiply sig row by next RAA rets row for realized return
  RAA_B_xsRets <- list()
  for(i in 1:(length(DFxsRets$stratSig)-1)) {
    
    returns <- as.numeric(DFxsRets$stratSig[i]) * as.numeric(DFxsRets$RAAbalMrets[i+1])
    RAA_B_xsRets[[i]] <- returns
    
  }#end Loop
  
  # Bind rows into a single column of Realized returns, len=60, class = list
  RAA_B_xsRets <- do.call(rbind, RAA_B_xsRets)
  
  # make xsRets into XTS object
  firstpart <- cbind(DFxsRets[2:length(stratSig)], RAA_B_xsRets)
  
  
  ### Rule 2 ,SMA10 on RAA balanced, if ret > SMA = 50% of Portfolio
  
  
  # Cum sum Raa monthly rets, sma10 on cum sum RAA rets
  cumRetsRAA <- cumsum(RAAbalancedMONTHLY)
  SMAcumRetsRAA <- SMA(cumRetsRAA, 10)
  
  # make Data Frame Cbind RAA rets, Cum sum rets and sma
  RAA_DF_sma<- na.omit(cbind(RAAbalancedMONTHLY, cumRetsRAA, SMAcumRetsRAA))
  colnames(RAA_DF_sma) <- c("RetsRAA","CumRetsRAA","SMA")
  
  
  #signal for sma strat, cum rets>sma
  #start loop create signal
  smaSig<- list()
  for(i in 1:length(RAA_DF_sma$RetsRAA)) {
    
    momDiff <- (as.numeric(RAA_DF_sma$CumRetsRAA[i]) - as.numeric(RAA_DF_sma$SMA[i])) > 0
    smaSig[[i]] <- momDiff
    
  }# end loop
  
  # Bind rows
  smaSig <- do.call(rbind, smaSig)
  
  
  #create Data Frame with signal and RAA rets
  RAA_DF_sma <- cbind(RAA_DF_sma, smaSig)
  
  
  # Start loop, multiply sig row by next RAA rets row for realized return
  RAA_B_smaRets <- list()
  for(i in 1:(length(RAA_DF_sma$RetsRAA)-1)) {
    
    returns <- as.numeric(RAA_DF_sma$smaSig[i]) * as.numeric(RAA_DF_sma$RetsRAA[i+1])
    RAA_B_smaRets[[i]] <- returns
    
  }#end Loop
  
  # Bind rows into a single column of Realized returns, len=60, class = list
  RAA_B_smaRets <- do.call(rbind, RAA_B_smaRets)
  
  
  # make SMA rets into XTS object
  secondpart <- cbind(RAA_DF_sma[2:length(smaSig)], RAA_B_smaRets)
  
  
  # Combine two strategy rets, 50% to each allocation, sum up parts
  TMOMrets <- firstpart$RAA_B_xsRets*.5
  SMArets <- secondpart$RAA_B_smaRets*.5
  RAA_B_rets <- TMOMrets + SMArets 
  colnames(RAA_B_rets) <- "RAA Balanced Returns"
```
A performance metric displaying calculated average- Annual Returns, Annual Standard Deviation, Annual Sharpe Ratio- Max Drawdown and Calmar Ratio. 
\smallskip
```{r results= "show",  message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

# compute strategy statistics, Ann Rets/ Ann SD/ Ann Sharpe/ Max DD/ Calmar Ratio
  stratStats <- function(rets) {
    stats <- rbind(table.AnnualizedReturns(rets), maxDrawdown(rets))
    stats[5,] <- stats[1,]/stats[4,]
    rownames(stats)[4] <- "Max Drawdown"
    rownames(stats)[5] <- "Calmar Ratio"
    return(stats)
  }
  stratStats(RAA_B_rets)

```
\newpage
Cumulative Return, Daily  Return histogram and Drawdown curve of the RAA strategy from Nov 2016 

\smallskip
```{r results= "show",  message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

 # Plot strat rets, monthly ret histogram and drawdown curve
  charts.PerformanceSummary(RAA_B_rets)
```
















