---
title: 'A Replication: The Trinity Portfolio- Meb Faber'
author: "Matthew Kiegerl"
date: "2/3/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\href{https://www.cambriainvestments.com/wp-content/uploads/2016/07/Trinity_DIGITAL_final.pdf} {The Trinity Portfolio} uses a basket of globally diverse asset classes and splits the portfolio into two parts $50/50$. The first is a passive buy and hold then re balanced monthly and where the weightings vary depending on your risk tolerance. 
\smallskip

The assets are ETFs and as follows. \newline


iShares MSCI USA Momentum Factorv (MTUM), \newline
iShares Russell 1000 Value (IWD), \newline
iShares MSCI EAFE Value (EFV), \newline
iShares MSCI Emerging Markets (EEM)\newline
iShares iBoxx Investment Grade Corporate Bond (LQD)\newline
iShares 20+ Year Treasury Bond (TLT), \newline
SPDR Bloomberg Barclays International Treasury Bond (BWX),\newline 
iShares TIPS Bond (TIP),\newline
iShares MSCI Emerging Markets (EEM)\newline
Invesco DB Commodity Index Tracking Fund (DBC)\newline
SPDR Gold Shares (GLD)\newline
Vanguard  Real Estate Index ETF (VNQ)\newline


The second part ranks the average of the 1/3/6/12 month cumulative returns from the assets and selects the top 5, then filters for if the price is above the 10 month SMA, those assets get evenly weighted $1/5$ in the portfolio and in cash if not. These three elements create the Trinity Portfolio. Following is and equity curve of the strategy from 2014-present, a histogram of monthly returns and and Drawdown curve.
 
\smallskip

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

require(quantstrat)

########### Replication of the Trinity Portfolio- Meb Faber ###################################################

### By: Matthew Kiegerl
  # 
  # In this illustration, I will attempt to replicate the Trinity Portfolio from
  # Meb Faber's 2015 white paper "The Trinity Portfolio" 
  #
  # The Trinity Portfolio is split into two equal halves.
  # The first invests in a static buy & hold allocation, 
  # and the second in a dynamic momentum/trend-following strategy.
  # 
  # First Part: Select from 11 Globally Diversified Asset Classes
  # Use momentum and value factor tilts to US equities, and a value tilt to international equities
  # 
  # Second Part: Apply simple momentum filter, select best half after 1/3/6/12m cum ret average
  # Apply trend following from filtered set, if asset > 10m SMA go long 1/5 else cash
  #
  # Note: MTUM and IWD will be weighted as the single US equity component evenly
  # 





##########################          #############################

  # 11 Global Asset Classes(ETF tickers) 
  tickers <- c("MTUM", # iShares MSCI USA Momentum Factor ETF
               "IWD", # iShares Russell 1000 Value ETF
               "EFV", # iShares MSCI EAFE Value ETF
               "EEM", # iShares MSCI Emerging Markets ETF
               "LQD", # iShares iBoxx Investment Grade Corporate Bond ETF
               "TLT", # iShares 20+ Year Treasury Bond ETF
               "BWX", # SPDR Bloomberg Barclays International Treasury Bond ETF
               "TIP", # iShares TIPS Bond ETF
               "DBC", # Invesco DB Commodity Index Tracking Fund
               "GLD", # SPDR Gold Shares
               "VNQ" # Vanguard  Real Estate Index ETF
               )  


  # Calculate returns from adjusted daily price data of ETFs from YAHOO, 
  # store in list bind columns, round to 5 decimal places
  rets <- list()
  for(i in 1:length(tickers)) {
    
    returns <- Return.calculate(Ad(get(getSymbols(tickers[i], from = '2000-01-01'))))
    colnames(returns) <- tickers[i]
    rets[[i]] <- returns
  }
  rets <- na.omit(do.call(cbind, rets))
  rets <- round(rets, 5)


  # Set weights for buy and hold part of strategy
  w = c(.09, .09, .135, .045, .198, .135, .144, .018, .05, .05, .045) 


  # calculate portfolio returns for passive part of portfolio
  port.rebal.monthly <- Return.portfolio(rets, weights = w, rebalance_on = "months")
  colnames(port.rebal.monthly) <- "Trinity Portfolio" 

  
  #### trend following part of strat ########################################################3

  # Get adjusted prices of ticker symbols, store in list, cbind data
  prices <- list()
  for(i in 1:length(tickers)) {
    
    ticker <- Ad(get(getSymbols(tickers[i], from = '2000-01-01')))
    colnames(ticker) <- tickers[i]
    prices[[i]] <- ticker
    
  }
  prices <- na.omit(do.call(cbind, prices))
  
  
  # create monthly price and return data from daily price data
  monthly.prices <- to.period(prices, period = "months", OHLC = FALSE)
  monthly.rets <- na.omit(Return.calculate(monthly.prices))


  # Calc 1-3-6-12 month rets, take average, rank the averages and select top 5, row bind data
  rankAssets <- list()
  
  for(i in 1:(length(monthly.rets$MTUM)-11)) {
    
    twelvemonths <- monthly.rets[c(i:(i+11)),]
    sixMonths <- monthly.rets[c((i+6):(i+11)),]
    threeMonths <- monthly.rets[c((i+9):(i+11)),]  
    oneMonth <- monthly.rets[c((i+11):(i+11)),]
    
    momentums <- (Return.cumulative(oneMonth) + 
                    Return.cumulative(threeMonths) +
                    Return.cumulative(sixMonths) + 
                    Return.cumulative(twelvemonths))/4
    
    highRankAssets <- rank(momentums) >= (length(tickers) - 4) # top 5 assets
    rankAssets[[i]] <- which(highRankAssets)
  }
  rankAssets <- do.call(rbind, rankAssets)


  # calculate 10 month simple moving average from monthly prices 
  allSMA <- list()
  
  for(i in 1:(length(tickers))) {
    
    movingAverages <- SMA(monthly.prices[,i], 10)
    colnames(movingAverages) <- tickers[i]
    colnames(movingAverages) <- paste("SMA10", colnames(movingAverages), sep = "_")
    allSMA[[i]]<- movingAverages
  }
  allSMA <- na.omit(do.call(cbind, allSMA)) 


  # Adjust monthly prices to same length as ranks matrix
  monthly.prices.adjDate <- monthly.prices[13:(length(monthly.prices$MTUM)),]


  # chose the ranked assets from monthly prices  
  chosenAssets <- list()
  for (i in 1:length(monthly.prices.adjDate$MTUM)) {
    
    chosenAssets[[i]] <- monthly.prices.adjDate[(i), rankAssets[i,]]
  }
  chosenAssets <-na.omit(do.call(rbind, chosenAssets))
  colnames(chosenAssets)<- NULL


  # adjust sma prices to length of ranks
  monthly.SMA.adjDate <- allSMA[4:(length(allSMA$SMA10_MTUM)),]

  
  # choose ranked SMA 
  chosenSMA <- list()
  for (i in 1:length(monthly.SMA.adjDate$SMA10_MTUM)) {
    
    chosenSMA[[i]] <- monthly.SMA.adjDate[(i), rankAssets[i,]]
  }
  chosenSMA <-na.omit(do.call(rbind, chosenSMA))
  colnames(chosenSMA)<- NULL  
  
  
  # adjust monthly rets to length of ranks
  monthly.rets.adjDate <- monthly.rets[12:(length(monthly.rets$MTUM)),]


  # get selected rets from ranks
  chosenRets <- list()
  
  for (i in 1:length(monthly.rets.adjDate$MTUM)) {
    
    chosenRets[[i]] <- monthly.rets.adjDate[(i), rankAssets[i,]]
  }
  chosenRets <-na.omit(do.call(rbind, chosenRets))
  colnames(chosenRets)<- NULL  


  # T/F df of signal  
  chosenSignal <- chosenAssets>chosenSMA

  
  #align rets df to signal
  stratDF <- cbind(na.omit(lag(chosenSignal)), chosenRets)
  stratDF <- stratDF[2:length(stratDF[,1])]


  # get returns from true signal
  signaledRets <- data.frame()
  
  for (i in 1:length(stratDF[,1])) {
    for (j in 1:5) {
      if(stratDF[i,j] == 1){
        signaledRets[i,j] <- as.numeric(stratDF[i,(j+5)])
      } else{
        signaledRets[i,j] <- 0
      }
    }
  }


  # Calc Trend part Returns, equal weight average of rets summation
  trendRets <- list()
  
  for (i in 1:length(signaledRets[,1])) {
    trendRets[[i]] <- sum(signaledRets[i,])/5
  }
  trendRets <- do.call(rbind, trendRets)


  # Calc rets from passive, adjust length
  passiveRets <- apply.monthly(port.rebal.monthly, FUN = sum)
  passiveRets <- passiveRets[1:length(passiveRets[,1])-1]
  passiveRets <- passiveRets[13:length(passiveRets[,1])]

  # cbind passive and trend
  trinity_Strat_DF <- cbind(passiveRets, trendRets)
  
  
  # Sum Passive and Trend and divide by 2 to get Trinity Portfolio Rets
  trinityStrat <- trinity_Strat_DF[,1]+trinity_Strat_DF[,2]
  trinityStrat <- (trinityStrat)/2
  colnames(trinityStrat) <- c("Trinity Portfolio")

```
A performance metric displaying calculated average- Annual Returns, Annual Standard Deviation, Annual Sharpe Ratio- Max Drawdown and Calmar Ratio. 
\smallskip
```{r results= "show",  message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

# compute strategy statistics, Ann Rets/ Ann SD/ Ann Sharpe/ Max DD/ Calmar Ratio
  stratStats <- function(rets) {
    stats <- rbind(table.AnnualizedReturns(rets), maxDrawdown(rets))
    stats[5,] <- stats[1,]/stats[4,]
    rownames(stats)[4] <- "Max Drawdown"
    rownames(stats)[5] <- "Calmar Ratio"
    return(stats)
  }
  stratStats(trinityStrat)

```
\newpage
Cumulative Return, Daily  Return histogram and Drawdown curve of the Trinity Portfolio from April 2014

\smallskip
```{r results= "show",  message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

 # Plot strat rets, monthly ret histogram and drawdown curve
  charts.PerformanceSummary(trinityStrat)
```









